---
title: "Demo HADACA3 Framework"
author: "Hugo Barbot and Florent Chuffart "
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
---

```{r, include=(FALSE)}
knitr::opts_chunk$set(collapse=TRUE, comment="#>", fig.width=9, fig.height=6, eval=TRUE, echo=TRUE, results="verbatim")
options(knitr.duplicate.label = "allow")
```

# Load data

Demo adapted from baseline_teamF and teamF_Source_prior_known_feature (attachment). Scripts are located here : https://gricad-gitlab.univ-grenoble-alpes.fr/hadaca3/hadaca3_private/-/tree/main/baselines/attachement?ref_type=heads, and were copied in the `src` folder. 

Data were downloaded from the HADACA3 challenge starting kit. 

```{r}
ref = readRDS("00_demo_data/data/reference_pdac.rds")
mix = readRDS("00_demo_data/data/mixes1_SBN5_pdac.rds")
source("scr/teamF_Source_prior_known_features.R")
```

# Block Preprocessing (PP)

Takes as input a multimodal .txt.gz, outputs a multimodal txt.gz

```{r}
program_blockPP <- function(mix_rna=NULL, ref_bulkRNA=NULL, 
                    mix_met=NULL, ref_met=NULL, ref_scRNA=NULL) {

   # Normalize input matrices
  if (normalisation)
  {
    ref_bulkRNA = normalize_matrix(ref_bulkRNA)
    ref_met = normalize_matrix(ref_met)
  }
  

  
  return() # MAG : je ne sais pas quoi sortir 
}


```

# Block Feature selection (FS)

Takes as input a multimodal .txt.gz, outputs a multimodal txt.gz

```{r}
program_blockFS <- function(mix_rna=NULL, ref_bulkRNA=NULL, 
                    mix_met=NULL, ref_met=NULL, ref_scRNA=NULL) {

     ## Drop all 0 references
  drop_null_ref_cols <- function(ref_matrix){
    non_null_rows = apply(ref_matrix != 0,MARGIN = 1, FUN = any, simplify = TRUE)
    return(ref_matrix[non_null_rows,])
  }
  ref_bulkRNA <- drop_null_ref_cols(ref_bulkRNA)
  
  return() # MAG : je ne sais pas quoi sortir 
}


```

# Block Deconvolution (D)

Takes as input a multimodal mix.txt.gz and a ref.txt.gz, output a prediction.txt.gz

MAG : question -> comment on gère ici qu'on va faire de la déconvolution sur chaque omique avant l'intégration tardive ?

```{r}
program_blockD <- function(mix_rna=NULL, ref_bulkRNA=NULL, 
                    mix_met=NULL, ref_met=NULL, ref_scRNA=NULL) {

    ## RNA:
  if ( !( is.null(x = mix_rna) ) ) {
    
    idx_feat = intersect(rownames(mix_rna), rownames(ref_bulkRNA))
    mix_rna = mix_rna[idx_feat,]
    ref_bulkRNA = ref_bulkRNA[idx_feat,]
    
    # Compute gene weights for Poisson like regression
    bulkRNA_weights <- if (weight) get_weights_poisson(ref_bulkRNA) else NULL
    
    if (rna_method == 'nnls')
    {
      if (weight) warning("bulk RNA reweighting not availaible for nnls, use lmw or rlr. Weights will be used only for late RMSE fusion.")
      prop_rna = get_prop_nnls(mix_rna, ref_bulkRNA)
    }
    else if(rna_method == 'lmw'){
      prop_rna = get_prop_lm(mix_rna, ref_bulkRNA, bulkRNA_weights)  
    }
    else if (rna_method == 'rlr')
    {
      prop_rna = get_prop_rlr(mix_rna, ref_bulkRNA, bulkRNA_weights)
    }
    else
    {
      print("Parametrisation error : you have to indicate which method to use for bulk RNA.")
      prop_rna = NULL
    }
  }
  
  ## Methylation:
  if ( !( is.null(mix_met) ) ) {
    
    idx_feat = intersect(rownames(mix_met), rownames(ref_met))
    mix_met = mix_met[idx_feat,]
    ref_met = ref_met[idx_feat,]
    
    if (met_method == 'nnls')
    {
      prop_met = get_prop_nnls(mix_met, ref_met)
    }
    else if (met_method == 'rlr')
    {
      ## with robust linear regression approach ----
      prop_met = get_prop_rlr(mix_met, ref_met)
    }
    else
    {
      print("Parametrisation error : you have to indicate which method to use for methylation.")
      prop_met = NULL
    }
    
  }
  
  

  
  return() # MAG : je ne sais pas quoi sortir 
}


```

# Block Late integration (LI)



Takes as input a a multimodal prediction.txt.gz, outputs an integrated prediction


```{r}
program_blockLI <- function(mix_rna=NULL, ref_bulkRNA=NULL, 
                    mix_met=NULL, ref_met=NULL, ref_scRNA=NULL) { # MAG : je ne sais pas quoi mettre en entrée qui cooresponde à la sortie de la déconvolution

   if ( !is.null(x = mix_met) ) {
    if ( !is.null(x = mix_rna) ) {
      
      stopifnot( identical(x = dim(prop_rna), y = dim(prop_met)) ) # stop if not same number of cell type or samples
      
      if (integration == 'rmse')
      {
        ## compute RMSE for rna and methylation estimation
        rmse_rna = rmse_mat(Y = as.matrix(mix_rna),
                            Y_estimate = ref_bulkRNA %*% prop_rna,
                            weights = bulkRNA_weights)
        rmse_met = rmse_mat(as.matrix(mix_met), ref_met %*% prop_met)
        
        ## initialize with basic values we will modify
        prop <- (prop_rna + prop_met) / 2
        for (i in 1:length(rmse_met))
        {
          prop_val = (prop_rna[,i] / rmse_rna[i] + prop_met[,i] / rmse_met[i]) / (1 / rmse_rna[i] + 1 / rmse_met[i])
          prop[,i] = prop_val
        }
      }
      else if (integration == 'EnsDeconv') {
        source("baselines/attachement/teamF_CTS_EnsDeconv_LS.R")
        list_proportions <- list("RNA" = t(prop_rna),
                                 "Met" = t(prop_met))
        
        prop <- t(CTS_EnsDeconv_LS(What = list_proportions, maxit = 1000)$W)
      }
      
      else
      {
        prop <- (prop_rna + prop_met) / 2
      }
      
    } else {
      prop <- prop_met
    }
  } else {
    prop <- prop_rna
  }
  
  if (any(colSums(prop) != 1)) { # Sum To One 
    prop <- sapply(
      1:ncol(prop), 
      function(col_i) { prop[,col_i] / sum(prop[,col_i]) }
    )
  }

  

  
  return(prop) # MAG : je ne sais pas quoi sortir 
}


```

# Session Information

```{r, results="verbatim"}
sessionInfo()
```
