---
title: "HADACA3 Framework - Generate data for data challenge hadaca"
subtitle: "Meta analysis"
author: ""
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
---

# Aggregated and atomic scores per method

```{r, echo=FALSE, eval=TRUE}
knitr::opts_chunk$set(collapse=TRUE, comment = "#>", fig.width=12, fig.height=12, eval=TRUE, echo=TRUE, results="verbatim", dpi=75)
```

```{r loading_pckgs ,echo=FALSE}
library(yaml)
library(DT)
library(stringr)
library(dplyr)
library(ggplot2)
theme_set(theme_light())

source(utils_script)
#source("utils/data_processing.R")
```



```{r Late_integration pipeline,echo=FALSE}


# datasets = read_yaml("datasets.yml") 
# print(score_file)

# datasets = read_yaml("datasets.yml") 
# datasets = read_yaml(file_dataset) 


list_wd = strsplit(getwd(),'/')[[1]]
# Snakemake script : the current working dir is hadaca3_framework
if(list_wd[length(list_wd)] == 'hadaca3_framework'){
  score_files = list(list.files(path = "./output/scores/", full.names = TRUE))

# nextflow script :
}else{
  score_files = list(list.files(pattern = 'score-li*' ))

}


results_li <- data.frame(
  dataset = character(),
  ref = character(),

  preprocessing_mixRNA = character(),
  feature_selection_mixRNA = character(),

  preprocessing_RNA = character(),
  feature_selection_RNA = character(),

  preprocessing_scRNA = character(),
  feature_selection_scRNA = character(),
  deconvolution_rna = character(),

  preprocessing_mixMET = character(),
  feature_selection_mixMET = character(),

  preprocessing_MET = character(),
  feature_selection_MET = character(),
  deconvolution_met = character(),
  late_integration = character(),
  
  aid = numeric(),
  aid_norm = numeric(),
  aitchison = numeric(),
  aitchison_norm = numeric(),
  jsd = numeric(),
  jsd_norm = numeric(),
  mae = numeric(),
  mae_norm = numeric(),
  pearson_col = numeric(),
  pearson_col_norm = numeric(),
  pearson_row = numeric(),
  pearson_row_norm = numeric(),
  pearson_tot = numeric(),
  pearson_tot_norm = numeric(),
  rmse = numeric(),
  rmse_norm = numeric(),
  score_aggreg = numeric(),
  sdid = numeric(),
  sdid_norm = numeric(),
  spearman_col = numeric(),
  spearman_col_norm = numeric(),
  spearman_row = numeric(),
  spearman_row_norm = numeric(),
  spearman_tot = numeric(),
  spearman_tot_norm = numeric()
)


i = 0 
for (score_file in score_files[[1]]) {
  # Extract the base name of the file

  base_name <- basename(score_file)

  # Extract components from the file name

  components <- str_match(base_name, 
  #       dt   ref  OMIC  ppmR fsmR omic ppR fsR omic  ppSR fsSR  deR   omic  ppmM fsmM omic ppM  fsM  deM  li
  "score-li-(.+)_(.+)_mixRNA_(.+)_(.+)_RNA_(.+)_(.+)_scRNA_(.+)_(.+)_(.+)_mixMET_(.+)_(.+)_MET_(.+)_(.+)_(.+)_(.+).h5")[2:16]
  
  
  # components <- str_match(base_name, "score-(.+)_(.+)_(.+)_(.+)_(.+)_(.+)_(.+)_(.+)")[2:8]
  scores <- read_hdf5(score_file)
  # Append the extracted information to the results data frame
  results_li <- rbind(results_li,
    cbind(
     data.frame(
       dataset = components[1],
       ref = components[2],

       preprocessing_mixRNA = components[3],
       feature_selection_mixRNA = components[4],

       preprocessing_RNA = components[5],
       feature_selection_RNA = components[6],

       preprocessing_scRNA = components[7],
       feature_selection_scRNA = components[8],
       deconvolution_rna = components[9],

        preprocessing_mixMET = components[10],
       feature_selection_mixMET = components[11],

       preprocessing_MET = components[12],
       feature_selection_MET = components[13],
       deconvolution_met = components[14],

       late_integration = components[15],
       stringsAsFactors = FALSE
     ),
     scores
    ))
  rownames(results_li) = NULL

  i = i +1 
}

results_li %>%
  # filter(dc==2) %>%
  group_by(late_integration) %>%
  summarise(GlobalScore = median(score_aggreg)) %>%
  arrange(desc(GlobalScore))



all_functions_li = c('preprocessing_mixRNA', 'feature_selection_mixRNA', 'preprocessing_RNA', 'feature_selection_RNA', 'preprocessing_scRNA', 'feature_selection_scRNA', 'deconvolution_rna', 'preprocessing_mixMET', 'feature_selection_mixMET', 'preprocessing_MET', 'feature_selection_MET', 'deconvolution_met', 'late_integration' )
for( fun in all_functions_li){
  results_li[[fun]] = factor(results_li[[fun]], 
  levels = unique(results_li[[fun]][order(results_li$score_aggreg[results_li$dataset=='invitro1'],decreasing = T)])) # sort based on the results_li on the in vitro dataset
}

all_data_used = c('dataset', 'ref')
for(data_used in all_data_used){
  results_li[[data_used]] = factor(results_li[[data_used]], 
  levels = unique(results_li[[data_used]])) # levels will be alphabeticaly ordered
}


index_aggreg <- which(names(results_li) == "score_aggreg")

datatable(
  results_li[, c(1:length(all_functions_li)+2, index_aggreg)],
  extensions = 'Buttons',
  options = list(
    pageLength = 10,
    dom = 'Bfrtip',  # This includes the Buttons extension in the layout
    buttons = list(
      list(
        extend = 'colvis',
        text = 'Show/Hide Columns',
        columns = ':not(:first-child)'  # This allows all columns except the first to be toggled
      )
    )
  )
)
```

```{r all_combinaisons_dataset_aff, echo=FALSE}
datatable(
  results[, c(1:length(all_functions)+2, index_aggreg)],
  extensions = 'Buttons',
  options = list(
    pageLength = 10,
    dom = 'Bfrtip',  # This includes the Buttons extension in the layout
    buttons = list(
      list(
        extend = 'colvis',
        text = 'Show/Hide Columns',
        columns = ':not(:first-child)'  # This allows all columns except the first to be toggled
      )
    )
  )
)
```


# Early integration_table 
```{r Early_integration pipeline,echo=FALSE}

list_wd = strsplit(getwd(),'/')[[1]]
# Snakemake script : the current working dir is hadaca3_framework
if(list_wd[length(list_wd)] == 'hadaca3_framework'){
  score_files = list(list.files(path = "./output/scores/", full.names = TRUE))

# nextflow script :
}else{
  score_files = list(list.files(pattern = 'score-ei*' ))

}


results_ei <- data.frame(
  dataset = character(),
  ref = character(),

  preprocessing_mixRNA = character(),
  feature_selection_mixRNA = character(),

  preprocessing_RNA = character(),
  feature_selection_RNA = character(),

  preprocessing_scRNA = character(),
  feature_selection_scRNA = character(),

  preprocessing_mixMET = character(),
  feature_selection_mixMET = character(),

  preprocessing_MET = character(),
  feature_selection_MET = character(),

  early_integration = character(),
  deconvolution = character(),
  
  aid = numeric(),
  aid_norm = numeric(),
  aitchison = numeric(),
  aitchison_norm = numeric(),
  jsd = numeric(),
  jsd_norm = numeric(),
  mae = numeric(),
  mae_norm = numeric(),
  pearson_col = numeric(),
  pearson_col_norm = numeric(),
  pearson_row = numeric(),
  pearson_row_norm = numeric(),
  pearson_tot = numeric(),
  pearson_tot_norm = numeric(),
  rmse = numeric(),
  rmse_norm = numeric(),
  score_aggreg = numeric(),
  sdid = numeric(),
  sdid_norm = numeric(),
  spearman_col = numeric(),
  spearman_col_norm = numeric(),
  spearman_row = numeric(),
  spearman_row_norm = numeric(),
  spearman_tot = numeric(),
  spearman_tot_norm = numeric()
)


i = 0 
for (score_file in score_files[[1]]) {
  # Extract the base name of the file

  base_name <- basename(score_file)

  # Extract components from the file name

  components <- str_match(base_name, 
  #        dt   ref  OMIC  ppmR fsmR omic ppR fsR omic  ppSR fsSR     omic  ppmM fsmM omic ppM  fsM  ei  de
  "score-ei-(.+)_(.+)_mixRNA_(.+)_(.+)_RNA_(.+)_(.+)_scRNA_(.+)_(.+)_mixMET_(.+)_(.+)_MET_(.+)_(.+)_(.+)_(.+).h5")[2:15]
  
  
  # components <- str_match(base_name, "score-(.+)_(.+)_(.+)_(.+)_(.+)_(.+)_(.+)_(.+)")[2:8]
  scores <- read_hdf5(score_file)
  # Append the extracted information to the results data frame
  results_ei <- rbind(results_ei,
    cbind(
     data.frame(
       dataset = components[1],
       ref = components[2],

       preprocessing_mixRNA = components[3],
       feature_selection_mixRNA = components[4],

       preprocessing_RNA = components[5],
       feature_selection_RNA = components[6],

       preprocessing_scRNA = components[7],
       feature_selection_scRNA = components[8],

        preprocessing_mixMET = components[9],
       feature_selection_mixMET = components[10],

       preprocessing_MET = components[11],
       feature_selection_MET = components[12],

       early_integration = components[13],
       deconvolution = components[14],

       stringsAsFactors = FALSE
     ),
     scores
    ))
  rownames(results_ei) = NULL

  i = i +1 
}

results_ei %>%
  # filter(dc==2) %>%
  group_by(early_integration) %>%
  summarise(GlobalScore = median(score_aggreg)) %>%
  arrange(desc(GlobalScore))


all_functions_ei = c('preprocessing_mixRNA', 'feature_selection_mixRNA', 'preprocessing_RNA', 'feature_selection_RNA', 'preprocessing_scRNA', 'feature_selection_scRNA', 'preprocessing_mixMET', 'feature_selection_mixMET', 'preprocessing_MET', 'feature_selection_MET', 'early_integration','deconvolution' )
for( fun in all_functions_ei){
  results_ei[[fun]] = factor(results_ei[[fun]], 
  levels = unique(results_ei[[fun]][order(results_ei$score_aggreg[results_ei$dataset=='invitro1'],decreasing = T)])) # sort based on the results_ei on the in vitro dataset
}

all_data_used = c('dataset', 'ref')
for(data_used in all_data_used){
  all_functions_ei[[data_used]] = factor(all_functions_ei[[data_used]], 
  levels = unique(all_functions_ei[[data_used]])) # levels will be alphabeticaly ordered
}


index_aggreg <- which(names(results_ei) == "score_aggreg")

datatable(
  results_ei[, c(1:length(all_functions_ei)+2, index_aggreg)],
  extensions = 'Buttons',
  options = list(
    pageLength = 10,
    dom = 'Bfrtip',  # This includes the Buttons extension in the layout
    buttons = list(
      list(
        extend = 'colvis',
        text = 'Show/Hide Columns',
        columns = ':not(:first-child)'  # This allows all columns except the first to be toggled
      )
    )
  )
)
```

# Visualisations of the different metrics


## Aggregated scores

### PP

```{r combinaisons_aggregated_scores_PP, echo=FALSE, eval=TRUE}
#### MET
boxplots_ppMET_aggreg = ggplot(results_li, aes(x = preprocessing_mixMET , y = score_aggreg, fill = preprocessing_mixMET)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Aggregated score (-> 1), per dataset",
    x = "Methods",
    y = "Aggregated score",
    fill = "Preprocessing for mixMET:"
  )
plotly::layout( # boxplotlys_ppMET_aggreg = 
  plotly::ggplotly(boxplots_ppMET_aggreg), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)


```{r combinaisons_aggregated_scores, echo=FALSE, eval=FALSE}
#### RNA
boxplots_pp_aggreg = ggplot(results_li, aes(x = preprocessing_mixRNA, y = score_aggreg, fill = preprocessing_mixRNA)) +

  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Aggregated score (-> 1), per dataset",
    x = "Methods",
    y = "Aggregated score",
    fill = "Preprocessing for mixRNA:"
  )
plotly::layout( # boxplotlys_ppRNA_aggreg = 
  plotly::ggplotly(boxplots_ppRNA_aggreg), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)

#plotly::subplot(boxplots_ppMET_aggreg, boxplots_ppRNA_aggreg, nrows=1) marche pas trop car pas 2 titres différents mais je pourrai essayer de mettre des sous-titres
```

### FS

```{r combinaisons_aggregated_scores_FS, echo=FALSE, eval=TRUE}
#### MET
boxplots_fsMET_aggreg = ggplot(results, aes(x = feature_selection_mixMET, y = score_aggreg, fill = feature_selection_mixMET)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Aggregated score (-> 1), per dataset",
    x = "Methods",
    y = "Aggregated score",
    fill = "Feature selection for mixMET"
  )
plotly::layout(
  plotly::ggplotly(boxplots_fsMET_aggreg), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)


#### RNA
boxplots_fsRNA_aggreg = ggplot(results_li, aes(x = feature_selection_mixRNA, y = score_aggreg, fill = feature_selection_mixRNA)) +

  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Aggregated score (-> 1), per dataset",
    x = "Methods",
    y = "Aggregated score",
    fill = "Feature selection for mixRNA:"
  )
plotly::layout(
  plotly::ggplotly(boxplots_fsRNA_aggreg), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)
```

### LI

```{r combinaisons_aggregated_scores_LI, echo=FALSE, eval=TRUE}

boxplots_li_aggreg = ggplot(results_li, aes(x = late_integration, y = score_aggreg, fill = late_integration)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Aggregated score (-> 1), per dataset",
    x = "Methods",
    y = "Aggregated score",
    fill = "Late integration"
  )
plotly::layout(
  plotly::ggplotly(boxplots_li_aggreg), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)
```


## MAE

### PP
```{r combinaisons_MAE_PP, echo=FALSE, eval=TRUE}
#### MET
boxplots_ppMET_mae = ggplot(results, aes(x = preprocessing_mixMET , y = mae, fill = preprocessing_mixMET)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Estimation error (-> 0), per dataset",
    x = "Methods",
    y = "MAE",
    fill = "Preprocessing for mixMET:"
  )
plotly::layout( # boxplotlys_ppMET_aggreg = 
  plotly::ggplotly(boxplots_ppMET_mae), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)

#### RNA
boxplots_ppRNA_mae = ggplot(results, aes(x = preprocessing_mixRNA , y = mae, fill = preprocessing_mixRNA)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Estimation error (-> 0), per dataset",
    x = "Methods",
    y = "MAE",
    fill = "Preprocessing for mixRNA:"
  )
plotly::layout( # boxplotlys_ppRNA_aggreg = 
  plotly::ggplotly(boxplots_ppRNA_mae), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)
```

### FS


#### MET
boxplots_fsMET_mae = ggplot(results_li, aes(x = feature_selection_mixMET, y = mae, fill = feature_selection_mixMET)) +

  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Estimation error (-> 0), per dataset",
    x = "Methods",
    y = "MAE",
    fill = "Feature selection for mixMET"
  )
plotly::layout(
  plotly::ggplotly(boxplots_fsMET_mae), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)


#### RNA
boxplots_fsRNA_mae = ggplot(results_li, aes(x = feature_selection_mixRNA, y = mae, fill = feature_selection_mixRNA)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Estimation error (-> 0), per dataset",
    x = "Methods",
    y = "MAE",
    fill = "Feature selection for mixRNA:"
  )
plotly::layout(
  plotly::ggplotly(boxplots_fsRNA_mae), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)
```

### LI

```{r combinaisons_MAE_LI, echo=FALSE, eval=TRUE}

boxplots_li_mae = ggplot(results_li, aes(x = late_integration, y = mae, fill = late_integration)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Estimation error (-> 0), per dataset",
    x = "Methods",
    y = "MAE",
    fill = "Late integration"
  )
plotly::layout(
  plotly::ggplotly(boxplots_li_mae), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)
```


## RMSE

### PP

```{r combinaisons_RMSE_PP, echo=FALSE, eval=TRUE}
#### MET
boxplots_ppMET_rmse = ggplot(results, aes(x = preprocessing_mixMET , y = rmse, fill = preprocessing_mixMET)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Root mean squared error (-> 0), per dataset",
    x = "Methods",
    y = "RMSE",
    fill = "Preprocessing for mixMET:"
  )
plotly::layout( # boxplotlys_ppMET_aggreg = 
  plotly::ggplotly(boxplots_ppMET_rmse), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)

#### RNA
boxplots_ppRNA_rmse = ggplot(results, aes(x = preprocessing_mixRNA , y = rmse, fill = preprocessing_mixRNA)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Root mean squared error (-> 0), per dataset",
    x = "Methods",
    y = "RMSE",
    fill = "Preprocessing for mixRNA:"
  )
plotly::layout( # boxplotlys_ppRNA_aggreg = 
  plotly::ggplotly(boxplots_ppRNA_rmse), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)
```

### FS


```{r combinaisons_RMSE_FS, echo=FALSE, eval=TRUE}
#### MET
boxplots_fsMET_rmse = ggplot(results_li, aes(x = feature_selection_mixMET, y = rmse, fill = feature_selection_mixMET)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Root mean squared error (-> 0), per dataset",
    x = "Methods",
    y = "RMSE",
    fill = "Feature selection for mixMET"
  )
plotly::layout(
  plotly::ggplotly(boxplots_fsMET_rmse), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)

#### RNA
boxplots_fsRNA_rmse = ggplot(results_li, aes(x = feature_selection_mixRNA, y = rmse, fill = feature_selection_mixRNA)) +

  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Root mean squared error (-> 0), per dataset",
    x = "Methods",
    y = "RMSE",
    fill = "Feature selection for mixRNA:"
  )
plotly::layout(
  plotly::ggplotly(boxplots_fsRNA_rmse), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)
```

### LI

```{r combinaisons_RMSE_LI, echo=FALSE, eval=TRUE}

boxplots_li_rmse = ggplot(results_li, aes(x = late_integration, y = rmse, fill = late_integration)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Root mean squared error (-> 0), per dataset",
    x = "Methods",
    y = "RMSE",
    fill = "Late integration"
  )
plotly::layout(
  plotly::ggplotly(boxplots_li_rmse), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)
```


## Spearman correlation (row)

### PP


```{r combinaisons_spearman_row_PP, echo=FALSE, eval=TRUE}
#### MET
boxplots_ppMET_spearman_row = ggplot(results_li, aes(x = preprocessing_mixMET , y = spearman_row, fill = preprocessing_mixMET)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Spearman cell types correlation (-> 1), per dataset",
    x = "Methods",
    y = "Spearman correlation (row)",
    fill = "Preprocessing for mixMET:"
  )
plotly::layout( # boxplotlys_ppMET_aggreg = 
  plotly::ggplotly(boxplots_ppMET_spearman_row), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)

#### RNA
boxplots_ppRNA_spearman_row = ggplot(results, aes(x = preprocessing_mixRNA , y = spearman_row, fill = preprocessing_mixRNA)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Spearman cell types correlation (-> 1), per dataset",
    x = "Methods",
    y = "Spearman correlation (row)",
    fill = "Preprocessing for mixRNA:"
  )
plotly::layout( # boxplotlys_ppRNA_aggreg = 
  plotly::ggplotly(boxplots_ppRNA_spearman_row), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)
```

### FS

```{r combinaisons_spearman_row_FS, echo=FALSE, eval=TRUE}
#### MET
boxplots_fsMET_spearman_row = ggplot(results, aes(x = feature_selection_mixMET, y = spearman_row, fill = feature_selection_mixMET)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Spearman cell types correlation (-> 1), per dataset",
    x = "Methods",
    y = "Spearman correlation (row)",
    fill = "Feature selection for mixMET"
  )
plotly::layout(
  plotly::ggplotly(boxplots_fsMET_spearman_row), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)


#### RNA
boxplots_fsRNA_spearman_row = ggplot(results_li, aes(x = feature_selection_mixRNA, y = spearman_row, fill = feature_selection_mixRNA)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Spearman cell types correlation (-> 1), per dataset",
    x = "Methods",
    y = "Spearman correlation (row)",
    fill = "Feature selection for mixRNA:"
  )
plotly::layout(
  plotly::ggplotly(boxplots_fsRNA_spearman_row), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)
```

### LI

```{r combinaisons_spearman_row_LI, echo=FALSE, eval=TRUE}

boxplots_li_spearman_row = ggplot(results_li, aes(x = late_integration, y = spearman_row, fill = late_integration)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Spearman cell types correlation (-> 1), per dataset",
    x = "Methods",
    y = "Spearman correlation (row)",
    fill = "Late integration"
  )
plotly::layout(
  plotly::ggplotly(boxplots_li_spearman_row), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)
```


## Aitchison distance

### PP

```{r combinaisons_aitchison_PP, echo=FALSE, eval=TRUE}
#### MET
boxplots_ppMET_aitchison = ggplot(results, aes(x = preprocessing_mixMET , y = aitchison, fill = preprocessing_mixMET)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Aitchison distance (-> 0), per dataset",
    x = "Methods",
    y = "Aitchison distance",
    fill = "Preprocessing for mixMET:"
  )
plotly::layout( # boxplotlys_ppMET_aggreg = 
  plotly::ggplotly(boxplots_ppMET_aitchison), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)


#### RNA
boxplots_ppRNA_aitchison = ggplot(results_li, aes(x = preprocessing_mixRNA , y = aitchison, fill = preprocessing_mixRNA)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Aitchison distance (-> 0), per dataset",
    x = "Methods",
    y = "Aitchison distance",
    fill = "Preprocessing for mixRNA:"
  )
plotly::layout( # boxplotlys_ppRNA_aggreg = 
  plotly::ggplotly(boxplots_ppRNA_aitchison), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)
```

### FS

```{r combinaisons_aitchison_FS, echo=FALSE, eval=TRUE}
#### MET
boxplots_fsMET_aitchison = ggplot(results, aes(x = feature_selection_mixMET, y = aitchison, fill = feature_selection_mixMET)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Aitchison distance (-> 0), per dataset",
    x = "Methods",
    y = "Aitchison distance",
    fill = "Feature selection for mixMET"
  )
plotly::layout(
  plotly::ggplotly(boxplots_fsMET_aitchison), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)


#### RNA
boxplots_fsRNA_aitchison = ggplot(results_li, aes(x = feature_selection_mixRNA, y = aitchison, fill = feature_selection_mixRNA)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Aitchison distance (-> 0), per dataset",
    x = "Methods",
    y = "Aitchison distance",
    fill = "Feature selection for mixRNA:"
  )
plotly::layout(
  plotly::ggplotly(boxplots_fsRNA_aitchison), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)
```

### LI

```{r combinaisons_aitchison_LI, echo=FALSE, eval=TRUE}

boxplots_li_aitchison = ggplot(results_li, aes(x = late_integration, y = aitchison, fill = late_integration)) +
  geom_boxplot() +
  facet_wrap(~ dataset, scales = "free_x") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  ) +
  labs(
    title = "Aitchison distance (-> 0), per dataset",
    x = "Methods",
    y = "Aitchison distance",
    fill = "Late integration"
  )
plotly::layout(
  plotly::ggplotly(boxplots_li_aitchison), 
  # boxmode = "group",
  legend = list(
    # x = 0,
    # y = -0.3,
    # xanchor = 'left',
    # yanchor = 'bottom',
    orientation = 'h')
)
```
